%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Dedicatória =====================================================================%
\newpage
\thispagestyle{empty}

 \parbox{5.4in}{
  \begin{center}
   \begin{flushright}
    \textit{This thesis is dedicated to Vó Isaura \\ a brave Northeastern lady \\ whose greatest dream was to see her grandchildren as Doctors.}
   \end{flushright}
  \end{center}
 }

\frontmatter
\newpage
%\thispagestyle{empty}


%==================================================================================%

% Verso ===========================================================================%
% \vspace*{8cm}

% \hspace{3cm}\parbox[c]{20cm}{{\it The path is the goal.}}
% \vspace{0.7cm}

% \hspace{4cm}{\footnotesize Mahatma Gandhi}

% \thispagestyle{empty}
%==================================================================================%

% Agradecimentos ==================================================================%
\newpage
%\thispagestyle{empty}
%\frontmatter

\bigskip
\bigskip
\begin{center}
{\Large{\bf Acknowledgments}}
\end{center}
\vspace{1cm}

\begin{quote}
Now that the project is almost over, I can see how much of an adventure taking a PhD course is. Our lives can change significantly in four years, as the world we live in.

Four years ago I met two people that I never imagined would make such a difference in my life. Both my supervisor Gustavo Dalpian and my co-supervisor Alexandre Reily Rocha showed me how to make interesting and quality science and revealed me a whole world of opportunities as a scientist. Despite of all the problems we face in this business, I cannot recall them ever saying that the efforts are not worthy, and their example as professionals and human beings is something that I will try to follow in many aspects of my life. 

We geeks and nerds have evolved and at this point of history we (or most of us) are not lonely creatures anymore. I would like to thank all my friends and colleagues that in many times helped and taught me a lot of things, sometimes not only related to science, and sometimes not related to anything serious at all. This list can be very long, so taking the chronological order, thanks to Luiz Zenko for convincing me to go to UFABC, Aline Schoenhalz for being the "boss" of us all and helping me with my first steps using VASP, Rodrigo "Digão" Amorim for teaching me the fine art of tinkering and compiling, Jorge Osorio-Guillén also for teaching a lot about pseudopotentials and DFT methods, Patricia Sawamura and Leonard Kubben for hosting me in the US and being fantastic friends, and Hannes Raebiger, Lumico and Soungmin Bae for all the babysitting when I was in Yokohama. Many colleagues and friends I would like to acknowledge just for the time we spent together in L605, IFT, or SSMT: Alexandre Ramalho, Raphael Silva, Juan Camilo Alvarez, Douglas Baquião, Fábio Negreiros, Elierge Costa, Igor Dias, Ygor Jacques, Cleiton Maciel, Tancredo Fontinelles, Tarciso Filho, Antenor Neto, Alvaro Torrez, Luana Pedroza, Jeconias Guimarães, Wudmir Rojas, César "Kike" Villegas, Ekaterina Filatova, Pedro Brandimarte, Santiago Pérez-Walton, Camilo Valencia-Balvín, Daisuke Yoshida, Misaki Iwaya, Masamichi Kaiba, Takuma Munehiro, Kuniaki Ono, and Swasti and her lovely family.

Family plays a decisive part in all this. All support and love I received from my wife Sayuri was mandatory to arrive at this point with my sanity (more or less) preserved. My father Antonio, who never got tired of answering "but why?", and my mother Tatiana, who always supported me in my path with all her love, were also largely responsible for this achievement. The support both me and my wife received from my parents in law Eiko and Ikiyoshi should also be acknowledged. Finally, the most important person, the one responsible for the great part of my studies is my grandmother Isaura, who always told me that her mission would be fulfilled when both me and my brother Yuri were doctors. Thanks \textit{Vó Isaura}.

This work would not be possible without the financial support by São Paulo Research Foundation - FAPESP. The funding through grants 2011/21719-8, 2015/05830-7, 2010/16202-3, and 2011/19924-2 was paramount for my survival, participation in conferences, and acquisition of necessary equipment. The professionalism shown by FAPESP in all circumstances should be taken as an example. Another team that deserves this very same recognition is the staff at Cenapad-SP, where many calculations presented here were performed.

Of course there is always much more than I can fit here. From the bus drivers, cleaning staff, cafeteria staff, administrative staff, security staff, library staff, the people (still) building UFABC, and many other (many times invisible) workers, my thanks.
\end{quote}

\newpage
\hspace{1cm}
\newpage
%==================================================================================%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
